%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}
\usepackage{etaremune}
\usepackage{tabularx}
%\pagestyle{plain}
%\pagestyle{myheadings}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
%\fancyhead{}
%\fancyfoot{}
%\fancyhead[LO,LE]{\textit{Curriculum Vitae --Brian A. Clark}}
%\fancyfoot[RO,RE]{\thepage}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}

\usepackage[left=0.7in,top=0.65in,right=0.7in,bottom=0.6in]{geometry} % Document margins
\name{Brian A. Clark} % Your name


%\address{B-1 \\ II , U.P. 208016} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
%\address{(+1)~7hh~9~8486 \\ x@ii.yzac.in} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	CONTACT
%----------------------------------------------------------------------------------------

%191 W. Woodruff Ave  \hfill  {\it Phone:}  (614) 247-8268 \\
%Physics Research Building   \hfill {\it Email:}  clark.2668@osu.edu \\ 
%The Ohio State University   \hfill {\it Website:} \url{u.osu.edu/clark.2668} \\ 
%Columbus, OH  43210 USA   \hfill {\it OrcID / inSPIRE:} \,\,      \href{https://orcid.org/0000-0003-4089-2245}{0000-0003-4089-2245}  / \href{https://inspirehep.net/author/profile/Brian.A.Clark.1}{Brian.A.Clark.1} \\ 
\vspace{-1cm}
%\begin{rSection}{CONTACT}
\rule{\textwidth}{0.1cm} \\ \\
\begin{tabular}{@{}p{2in}p{4in}}
1620 N. High Street, Apt 422             & {\it Phone:}  (314) 365-2605 \\            
Columbus, OH 43201  & {\it Email:}  baclark7777@gmail.com \\   
\end{tabular}
%\end{rSection}
%\vspace{0.25cm}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%---------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}
Leverage my 5+ years of experience building, simulating, and analyzing data from radio-frequency based scientific instruments to solve critical electrophysics problems in aerospace applications.
\end{rSection}
%\vspace{-0.1cm}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------


\begin{rSection}{EDUCATION}
\textbf{Ph.D in Physics, The Ohio State University}, Columbus, OH \hfill 2019 (Expected)\\
\vspace*{-.2in}

\textbf{M.S. in Physics, The Ohio State University}, Columbus, OH \hfill 2016 \\
\vspace*{-.2in}

\textbf{B.A. in Physics, \textit{cum laude}, Washington University}, St. Louis, MO \hfill 2014\\
\vspace*{-.2in}
\end{rSection}
%\vspace{-0.1cm}

%----------------------------------------------------------------------------------------
%	RELEVANT SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS and AWARDS}

\begin{tabular}{@{}l l l@{}}
Programming/Software & & C++/C, Python, Bash/Shell, R, Matlab \\ 
Mechanical/Electrical & & Surface mount soldering, power distribution, RF signal conditioning  \\ 
Technical & & Grant Writing, Statistics, Calculus, Linear Algebra, Electromagnetism\\
\end{tabular}

National Science Foundation Graduate Research Fellowship \hfill 2016-2019 \\
OSU Graduate Enrichment Fellowship \hfill 2014-2015
\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}
{\bf Ph.D. Research Fellow, The Ohio State University}, Columbus, OH \hfill {\bf Aug 2014 - present}\\
{\em Research Focus: Ultra-High Energy Neutrino Astrophysics with Radio-Based Detectors}
\begin{itemize}
\vspace*{.05in}
\item {\bf Developed novel frequency and time-series analysis techniques for MHz RF data} and applied those techniques in analyses of radio emission from solar flares (\href{https://arxiv.org/abs/1807.03335}{[published in 2018]}).
\item {\bf Implemented filtering and phasing techniques to remove human-made noise from RF data}, and applied those techniques in a low-SNR search for neutrinos in an large 80TB data set. 
\item {\bf Lead the mechanical and electrical systems integration} of three neutrino detecting stations, including {\bf managing the budget and equipment acquisition}, and supervising a three person team of junior students.
\item Deployed to Antarctica for five weeks to lead the commissioning and calibration of five neutrino detecting stations; performed rapid on site assessment of instrument performance.
\item {\bf Created and managed automated quality control software} for a large Monte Carlo simulation package, supporting a team of several dozen international scientists.
\end{itemize}

{\bf Teaching Assistant, The Ohio State University}, Columbus, OH \hfill {\bf Aug 2015 - Aug 2016}
\begin{itemize}
\item Aug 2016: Facilitated two-day ``introduction to teaching and learning`` workshop for 30 first-time Teaching Assistants; guided development of teaching identities and planning for classroom success.
\item Spring 2016: Served as teaching assistant for 80 student introductory survey course; designed evaluation instruments and moderated online student forum.
\item Fall 2015: Guided student learning in the recitation and laboratory context; facilitated quantitative laboratory experiments including team-based problem solving exercises.

\end{itemize}

\end{rSection}

\end{document}
